%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer Engineer II} % Job title
    {Amazon} % Organization
    {London, U.K} % Location
    {Dec. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing live system working at scale of 500K requests per seconds and designing new features which can scale up the system even further.}
        \item {Added support for native AWS clients to call internal servers using OAuth 2.0 based authorisation and authentication.}
        \item {Also provide a mechanism for having a dynamic client configuration across the fleet to support fine grain access control and throttling for the clients on the fly.}
        \item {Upgraded the metadata framework which allows ingestion of new attributes and running validations on the fly, giving faster feedback to our costumers.}
        \item {Designed a new caching framework which more than doubled the system performance while also being more resilient. The new design decreased the latency of UI operations on client side.}
        \item {Full stack software developer working on Amazon's website used by sellers and vendors to manage their products.}
        \item {Learned to develop and manage systems at scale keeping customers first.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {FactSet} % Organization
    {London, U.K} % Location
    {Aug. 2016 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing and working on website and REST based API which allows users to create, save, schedule and view their complex workflows and run them based on time or other event based triggers.}
        \item {Managing and upgraded an existing technology which is used to generate dynamic web pages and templates on the fly.}
        \item {Implemented many critical fixes and speedups to improve performance and stability.}
		\item {Using source control techniques like GIT and Perforce for better team collaboration globally.}
        \item {Gained a good insight into the financial side of technological development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Summer Intern} % Job title
    {FactSet} % Organization
    {London, U.K} % Location
    {June 2015 - Sept. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked for FactSet Market Fundamentals.}
        \item {Upgraded an existing Perl based system’s functionality and scalability. Gained knowledge and experience in Perl, database techniques.}
        \item {Got a good insight in different database technologies. Followed agile and scrum methodology and learned some good coding practices.}
        \item {Developed better communication and team-working skills while working in a team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Ambassador - Science and Engineering Family Day} % Job title
    {University of Southampton} % Organization
    {Southampton, U.K} % Location
    {March 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed interpersonal and communication skills by discussing ideas and answering enquiries.}
        \item {Our team was selected as a winner in the STEM institution category.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
