%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------

    \cventry
    {\textbf{Hybrid Image Learning and Classification Architecture}} % Job title
    {}
    {}
    {Oct. 2015 - March 2016} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    	\item { Designed and developed a hybrid novel architecture which shall speed up image classification and facilitate future upgrades. It uses deep-neural networks (Caffe framework) along with SVMs and other AI techniques (OpenCV framework) and uses MongoDB database at its core. }
    \end{cvitems}
    }

	%---------------------------------------------------------

	
	%---------------------------------------------------------
	
	\cventry
	{\textbf{Web-Application for Food Management}} % Job title
	{}
    {}
    {Nov. 2015 - Jan. 2016 }
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
        \item Created a web application in a team which helps users to save food and suggest recipes based on groceries they already have. Application hosted on google-cloud based on Python, JavaScript and Angular. (
    	%\urlstyle{same}
    	\url{https://cloudappdevg.appspot.com}
    	)
	\end{cvitems}
	}
	
	%---------------------------------------------------------
	
	
	%---------------------------------------------------------
	
	\cventry
	{\textbf{Custom compiler and functional language}} % Job title
	{}
    {}
    {March. 2015 - June. 2016}
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
	    \item Designed and implemented a custom compiler written in OCaml for our own language, in pair. Created an evaluator for Scheme which helped me gain valuable insight into functional programming.
	\end{cvitems}
	}
	
	%---------------------------------------------------------
	
	
	%---------------------------------------------------------
	
	\cventry
	{\textbf{AI Game Solver}} % Job title
    {}
    {}
    {Oct. 2014 - Dec. 2014}
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
	    \item Created an AI game solver which solves the 8 / 16 puzzle. Created both Heuristic and Blind searches.
	\end{cvitems}
	}
	
	%---------------------------------------------------------

	
	%---------------------------------------------------------
	
	\cventry
	{\textbf{Java based projects}} % Job title
	{}
    {}
    {Oct. 2013 - June. 2015}
	{
	\begin{cvitems} % Description(s) of tasks/responsibilities
	    \item Designed and Built a complete Auction \& Messaging system (Both server and front end application), Distributed power system chain (Smart Meter), Fractal creation algorithm and underlying GUI, Bee hive Simulation. Also in group of 4 people, we designed and created an Advertisement dashboard which has many complex features presented with a fully functional UI (Using Agile Methodologies)
	\end{cvitems}
	}
	
	%---------------------------------------------------------

\end{cventries}
